{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-29 paper.tex
Mkae lualatex happy
Minor language

\pdfinfo{
   /Author (Hidden for blind review)
   /Title  (underwords: Cascading Situation Assessment for Robots)
   /CreationDate (D:20180115162200)
   /Subject (Robots)
   /Keywords (Situation Assessment;Perspective Taking)
}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{performances}
    \caption{Propagation times of one change (node creation)
    across $n$ worlds. The test is performed by running $n-1$ pass-through
    filters (independent processes) which each monitor one world and replicate
    any change into the next world. Times measured over 20 trials, performed on
    a 8 core machine.}
    \label{fig|performances}
\end{figure}

>>>>

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{performances}
    \caption{Propagation times of one change (node creation)
    across $n$ worlds. The test is performed by running $n-1$ pass-through
    filters that monitor one world and replicate
    any changes into the next world. Durations measured over 20 runs, performed on
    a 8 core machine.}
    \label{fig|performances}
\end{figure}
